### 2020-10-09 versao_09_10_2020/09_10_2020.tex
versão com linhas das tabelas corrigidas

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
%\usepackage[dvips]{graphicx, color}
%\usepackage{subfigure}
%\usepackage[skins,listings,breakable]{tcolorbox}
\usepackage{xcolor}
\usepackage{color}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}

@@

@@

\begin{abstract}\noindent
This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

\vspace{0.5in}
\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\

@@

The mechanism by adding shape parameters to a baseline distribution has
proved to be useful to make the generated distributions more flexible especially for studying tail
properties than existing distributions and for improving their goodness-of-fit statistics
to the data under study. Many special distributions in these families are discussed by Tahir
and Nadarajah (2015).

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
parameter vectot $\eta$. A generalized family are presented
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators. These families are important for modeling data
in several engineering areas.

@@

For $\theta=1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$. 
Equation \eqref{densityMO} represents the PDF of the minimum of $n$ iid random variables having density $g(x)$, say $T_1,\cdots,T_N$, 
where $N$ has a geometric distribution with probability parameters $\theta$ and $\theta^{-1}$ if $0<\theta<1$ and $\theta>1$, 
respectively.

Tahir and Nadarajah (2015, Table 2) presented thirty distributions
belonging to this family. It is easily generated from the baseline quantile function (QF) by
$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

@@

Each new $\Gamma$-G distribution follows from a given baseline G.
For $a=1$, the $\Gamma$-G family reduces to G.
If $Z$ is a gamma random variable with unit scale
parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.

The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
family and presents some special models. The maximum likelihood estimates (MLEs) of the parameters of the new family is addressed
in Section \ref{estimation}. Some simulations ate performed in Section \ref{sec:simulation} to estimate the biases of the MLEs. Two
empirical applications illustrate the potentiality of the proposed family in Section \ref{applications}. A variety of theoretical properties are derived
in Section \ref{properties}. Some conclusions remarks are offered in Section \ref{conclusions}.

@@

By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G
representing the new family is defined by
\begin{equation}\label{CDF_MO-Gamma-G}
F_{X}(x)=\frac{\gamma_1\left( a, -\log \left[1-G(x)\right]\right)}{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)},\quad x \in \mathbb{R}.
\end{equation}

By differentiating (\ref{CDF_MO-Gamma-G}), the PDF of $X$ follows as
\begin{equation}\label{PDF_MO-Gamma-G}
f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}}.
\end{equation}

@@

Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
more flexibility for these functions in relation to the baseline ones.

@@

The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,10$, in terms of the baseline QF $Q_G(\cdot)$. The inverse of
$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
of Equations (\ref{CDF_MO})and \eqref{CDF_MO-Gamma-G}, $F_{X}(x)=u$ leads to
$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$.
Then, the QF of $X$ can be expressed as
$$x=Q_G\left(v(u)\right),$$
where
$$v(u)=1-\exp\left[-\gamma_1^{-1}\big(a,z(u)\big)\right],$$
and $\gamma_1^{-1}(a,w)=Q^{-1}(a,1-w)$ is the inverse function of $\gamma_1(a,w)$. Some formulae for
$Q^{-1}(a,1-w)$ are given in \url{http:// functions.wolfram.com/ GammaBetaErf/ InverseGammaRegularized/}.

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special Distributions in the  MO-$\Gamma$-G family.}
\end{table}
\end{landscape}

@@

The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
and the formal statistics defined in Section \ref{applications}. It is necessary to provide the
PDF and CDF of the distribution to be fitted to a data set.

For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations is
\begin{align}\label{loglik}
\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}\nonumber \\ &
-n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
\end{align}

Due to the impossibility of obtaining the MLEs in closed form, numerical methods to obtain the estimates that maximize $ \ell (\cdot) $ are necessary. Several programming languages and statistical software distributes functions and routines that make it easy to obtain numerical estimates by various interactive methods. In practice, obtaining the MLEs for the parameters that index a probability distribution are commonly obtained in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.

To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020). This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.  With it, in particular using the goodness.fit function, it is possible to provide an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of this function, obtain $\ell(\cdot)$  by returning several measures of fit adequacy as well as the MLEs. Further details regarding this package can be obtained from Marinho et al. (2019).

@@

Due to the probable absence of MLEs in closed-form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to examine the
precision of the estimates calculated numerically. For doing that, the biases of the estimators of the parameters of the
MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
is the baseline distribution. All parameters are taken equal to one for different sample sizes reported in Table \ref{tab:bias}.

Ten thousand Monte Carlo simulations are performed for each sample size to examine the numerical estimates calculated by the
BFGS method. The figures in Table \ref{tab:bias} indicate that this method behaves well when the sample size increases.
This is theoretically expected. However, in practice, difficulties can be faced in other families of distributions
due to the flatness of the log-likelihood function.

All simulations can be reproduced using the script in Appendix \ref{ap:simulation}. The simulations are parallelized and able to use all threads
available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
The simulations are performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz,
requiring, on these hardware, a time of 14.36 hours to perform all simulations. The figures in Table \ref{tab:bias} reveal that the average
biases of the MLEs could be very reduced only for $n> 2,000$.

To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies. For doing this, another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$. Then, the acceptance and rejection algorithm is defined by the following steps:
\begin{enumerate}
	\item Generate an outcome $y$ from $Y$;
	\item Generate an observation $u$ from a random variable $U\sim \mathcal{U}(0,1)$;
	\item If $u < \frac{f(y)}{c\, g(y)}$, where $c$ is a real constant, accept $x=y$; otherwise reject $y$ as an outcome from $X$ and return to 1.
\end{enumerate}

The constant $c$ must be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $. 
Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen 
as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).

@@

Consider the Weibull baseline. Two applications are provided to compare the new generated model with seven extended Weibull
distributions, namely the beta-Weibull ($\beta$-W) (Famoye {\it et al.}, 2005), Kumaraswamy Weibull (Kw-W) (Cordeiro and Nadarajah, 2010),
Marshall-Olkin Weibull (MO-W) (Ahmed {\it et al.}, 2017), Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro {\it et al.}, 2019),
exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) Cordeiro {\it et al.}, 2016) and exponentiated
generalized Weibull (EG-W) (Oguntunde {\it et al.}, 2015) (with $a=1$). Some of these distributions are widely used in practice.

@@

For the first data set, a modification of the ``FoodExpenditure'' data from the {\bf betareg} package  is considered, which refers
to the proportions of income spent on food for a random sample of 38 households in a large US city (according to the package information).
Here, the household expenditures for food are considered and is given by
\begin{eqnarray*}
data = FoodExpenditure_{food} / \#(FoodExpenditure_{food}),
\end{eqnarray*}
where $FoodExpenditure_{food}$ is the random variable corresponding to the household expenditures for food and $\#(\cdot)$ indicates the number of
observations on this variable. The MLEs and their standard errors (SEs) (in parentheses) are listed in Table \ref{tab-ex1}.
The statistics  W$^{*}$ and A$^{*}$ are also given in this table. The results indicate that the proposed model has better performance than the other
seven fitted models.

@@

As a second application, consider a data set collected in a pilot study about hypertension in the Dominican Republic
in 1997 found in \url{http://biostat.mc.vanderbilt.edu/wiki/
Main/DataSets}. The observations are the systolic blood pressure of persons who came to medical clinics in
several villages for a variety of complaints. The MLEs of the parameters, their SEs and the values of the statistics are
listed in Table \ref{tab-ex2} for the previous distributions. By comparing the measures of these formal statistics,
we conclude that the proposed distribution outperforms the rest of them.

@@

In this section, some main mathematical properties are presented for the MO-$\Gamma$-G family
based on a general linear representation for its density function, which are important
to determine its mathematical properties from those of exponentiated-G (exp-G) distributions.

@@

So, some structural properties of the proposed family can be determined from the double linear combination (\ref{lcom})
and those properties of the exp-G distribution. In most applications, the indices $i$ and $j$ can vary up to five.

@@

A new family of distributions called the Marshall and Olkin-Gamma-G family with two shape parameters is introduced. The estimation of the unknown
parameters is done via the maximum likelihood method and a simulation study is conducted to verify its adequacy. Additionally, the usefulness
of the proposed family is shown empirically by means of two applications to real data.

>>>>

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
%\usepackage[dvips]{graphicx, color}
%\usepackage{subfigure}
%\usepackage[skins,listings,breakable]{tcolorbox}
\usepackage{xcolor}
\usepackage{color}
\usepackage{xurl}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}

@@

\usepackage[hmargin=2.3cm,vmargin=2.3cm,bindingoffset=0.5cm]{geometry}

@@

\begin{abstract}\noindent
This article introduces a new family of distributions by combining the Marshall and Olkin-G and Gamma-G classes.
The family has only two extra shape parameters and can be a better model than other well-known classes of distributions.
Simulations are performed to illustrate the consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

\vspace{0.5in}
\noindent {\bf Key Words}: Adequacy model package; Marshall and Olkin distribution; R language; Weibull distribution\\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
E-mail:\emph{gauss@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\

@@

The mechanism by adding shape parameters to a baseline distribution has
proved to be useful to generate more flexible distributions, study their
mathematical properties and improve the goodness-of-fit statistics
to the data under study. Many special distributions in these recent families are discussed by Tahir
and Nadarajah (2015).

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the corresponding probability density function (PDF)
depending on a parameter vector $\eta$. A generalized family is introduced here
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators, which is important important
for modeling data in several applied areas.

@@

For $\theta=1$, $f_{\text{MO-G}}(x)$ is just equal to $g(x)$.
Equation \eqref{densityMO} represents the PDF of the minimum of $n$ independent and identically distributed (iid) random variables
having density $g(x)$, say $T_1,\cdots,T_N$, where $N$ has a geometric distribution with probability parameters $\theta$ and $\theta^{-1}$
if $0<\theta<1$ and $\theta>1$, respectively.

Tahir and Nadarajah (2015, Table 2) presented thirty distributions
belonging to this family. It can be easily generated via the quantile function (QF) of G as
$Q_{
\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

@@

Each new $\Gamma$-G distribution follows from a specified baseline G. For $a=1$, the $\Gamma$-G family
reduces to G. Let $Z$ be a gamma random variable with unit scale and shape parameter $a>0$; then $W=Q_G(1-\rm{e}^{Z})$
has density (\ref{PDF_Ga}). So, the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.

The remainder of this paper is organized as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
families and presents some special models. The maximum likelihood estimates (MLEs) is addressed
in Section \ref{estimation}. Some simulations are reported in Section \ref{sec:simulation} which provide numerical evidence on the biases
of the estimators in finite samples. Two empirical applications show the potentiality of the new family in
Section \ref{applications}. Some structural properties are derived in Section \ref{properties}.
Conclusions remarks are offered in Section \ref{conclusions}.

@@

By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G of the new family is defined by
\begin{equation}\label{CDF_MO-Gamma-G}
F_{X}(x)=\frac{\gamma_1\left( a, -\log \left[1-G(x)\right]\right)}{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)},\quad x \in \mathbb{R}.
\end{equation}

By differentiating (\ref{CDF_MO-Gamma-G}), the PDF of $X$ can be expressed as
\begin{equation}\label{PDF_MO-Gamma-G}
f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}}.
\end{equation}

@@

Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard
functions of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) are displayed in Figure \ref{formas}, which provide
more flexibility for these functions in relation to the baseline ones.

@@

The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
say $x=Q_{X}(u)=F_X^{-1}(u)$ in terms of $Q_G(\cdot)$, where $u$ is a uniform number in $(0,1)$.
The inverse of $F_{X}(x)=u$ is easily obtained by combining the inverses
of Equations (\ref{CDF_MO}) and \eqref{CDF_MO-Gamma-G}. Equation $F_{X}(x)=u$ leads to
$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$,
and then the QF of $X$ has a simple form
$$x=Q_G\left(v(u)\right),$$
where
$$v(u)=1-\exp\left[-\gamma_1^{-1}\big(a,z(u)\big)\right],$$
and $\gamma_1^{-1}(a,w)=Q^{-1}(a,1-w)$ is the inverse function of $\gamma_1(a,w)$. Some formulae for
$Q^{-1}(a,1-w)$ are given in \url{http:// functions.wolfram.com/ GammaBetaErf/ InverseGammaRegularized/}.

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(x/\beta)^\alpha),\,\alpha,\beta>0$ & $f_X(x)=\frac{\alpha \theta x^{\alpha-1}\,[(x/\beta)^{\alpha}]^{a-1}\,\exp[-(x/\beta)^{\alpha}]}{\beta^{\alpha}\,\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(x/\beta)^\alpha]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special distributions in the  MO-$\Gamma$-G family.}
\end{table}
\end{landscape}

@@

The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
This packa\-ge does not require the log-likelihood function and it computes the MLEs, their standard errors (SEs)
and the formal statistics defined in Section \ref{applications}. It is only necessary to provide the
PDF and CDF of the distribution to be fitted to a data set.

If $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations is
\begin{align}\label{loglik}
\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}\nonumber \\ &
-n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
\end{align}

Due to the impossibility of obtaining the MLEs in closed form, numerical methods to maximize $ \ell (\cdot) $ are necessary.
Several programming languages and statistical software provides functions and routines that make it easy to obtain numerical estimates by various
interactive methods. In practice, obtaining the MLEs for the parameters that index a distribution are commonly obtained in this way,
since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.

To obtain the MLEs, the {\bf AdequacyModel} package of the programming language {\sf R} was used, see R Core Team (2020). This library,
created and updated by one of the authors of this paper, is widely cited by several papers in Statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN. By using the goodness.fit function, it provides an implementation of (\ref{PDF_MO-Gamma-G})
in {\sf R} giving $\ell(\cdot)$ by returning the MLEs and some adequacy measures of fit.
Further details regarding this package can be obtained from Marinho et al. (2019).

@@

Due to the probable absence of MLEs in closed-form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to examine the
precision of the estimates calculated numerically. For doing that, the biases of the estimators of the parameters of the
MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are calculated, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
is the baseline distribution. All parameters are taken equal to one for different sample sizes reported in Table \ref{tab:bias}.

Ten thousand Monte Carlo simulations are performed for each sample size to calculate the estimates by the
BFGS method. The figures in Table \ref{tab:bias} indicate that this method behaves well when the sample size increases.
This is theoretically expected. However, in practice, difficulties can be faced in other families of distributions
due to the flatness of the log-likelihood function.

All simulations can be reproduced using the script in Appendix \ref{ap:simulation}. The simulations are parallelized and able to use all threads
available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
The simulations are performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz,
requiring, on these hardware, a time of 14.36 hours to perform all simulations. The figures in Table \ref{tab:bias} reveal that the average
biases of the MLEs could be very reduced only for $n>1,000$.

To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies. For doing this, another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$. Then, the acceptance and rejection algorithm is defined by the following steps:
\begin{enumerate}
	\item Generate an outcome $y$ from $Y$;
	\item Generate an observation $u$ from a uniform random variable $U$ in $(0,1)$;
	\item If $u < \frac{f(y)}{c\, g(y)}$, where $c$ is a real constant, accept $x=y$; otherwise reject $y$ as an outcome from $X$ and return to 1.
\end{enumerate}

The constant $c$ should be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $.
Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$,
$c$ is chosen as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).

@@

Consider the Weibull baseline. Two applications are provided to compare the new generated model with seven extended Weibull
distributions, namely the beta-Weibull ($\beta$-W) (Famoye {\it et al.}, 2005), Kumaraswamy Weibull (Kw-W) (Cordeiro and Nadarajah, 2010),
Marshall-Olkin Weibull (MO-W) (Ahmed {\it et al.}, 2017), Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro {\it et al.}, 2019),
exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) (Cordeiro {\it et al.}, 2016) and 
exponentiated generalized Weibull (EG-W) (Oguntunde {\it et al.}, 2015) (with $a=1$). Some of these distributions are widely used in practice.

@@

For the first data set, a modification of the ``FoodExpenditure'' data from the {\bf betareg} package  is considered, which refers
to the proportions of income spent on food for a random sample of 38 households in a large US city.
Here, the household expenditures for food are given by
\begin{eqnarray*}
data = FoodExpenditure_{food} / \#(FoodExpenditure_{food}),
\end{eqnarray*}
where $FoodExpenditure_{food}$ is the random variable corresponding to the household expenditures for food and $\#(\cdot)$ indicates the number of
observations on this variable. The MLEs, their standard errors (SEs) (in parentheses) and the adequacy statistics are listed in Table \ref{tab-ex1}.
The proposed model has a better fit to the data than the others.

@@

As a second application, the systolic blood pressure of persons collected in a pilot study about hypertension in the Dominican Republic
in 1997 found in \url{http://biostat.mc.vanderbilt.edu/wiki/
Main/DataSets} are analyzed. The MLEs, their SEs and the values of the statistics are
reported in Table \ref{tab-ex2}. The proposed distribution outperforms the rest of them by comparing the measures of these formal 
statistics.

@@

Some main mathematical properties are addressed for the MO-$\Gamma$-G family
based on a general linear representation for its density function and those properties 
of exponentiated-G (exp-G) distributions.

@@

So, some structural properties of the proposed family can be found from the double linear combination (\ref{lcom})
and those properties of the exp-G distribution. In most applications, the indices $i$ and $j$ can vary up to five.

@@

A new family of distributions called the Marshall and Olkin-Gamma-G family with two shape parameters is introduced. The estimation of the unknown
parameters is done via maximum likelihood and a simulation study is conducted to verify its adequacy. Additionally, the usefulness
of the proposed family is shown empirically using two real data sets.
